---
title: "Netflix_EDA"
author: "Casey Franco"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

# File Info
I downloaded this file from the following address on [Kaggle](https://www.kaggle.com/datasets/risakashiwabara/netfllix-weekly-views-data)

It contains information about weekly Netflix user viewership.

# Importing and Defining "Value Counts" Function
```{r}

df <- read.csv("/Users/caseyfranco/Desktop/Data Science Resources/Datasets for Visualization/Netflix Viewership/all-weeks-global.csv")

value_counts <- function(x, sort = FALSE) {
  counts <- table(x)
  if (sort) {
    counts <- counts[order(-counts)]
  }
  return(counts)
}

head(df)
```
# Summary Statistics
```{r}
summary(df)
str(df)
```

# Distribution Visualization
I'll plot some histograms to see how the variables are distributed.
```{r}
hist(df$weekly_rank, main = "Weekly Rank Distribution", xlab = "Weekly Rank")
value_counts(df$weekly_rank, sort = TRUE)
```
It would appear that there is an even distribution of weekly ranks for shows. Exactly 528 entries for each rank. Not much I can garner there except that this dataset is likely curated.

```{r}
library(ggplot2)
hist(df$weekly_hours_viewed, main = "Weekly Hours Viewed Distribution", xlab = "Weekly Hours Viewed")
ggplot(df, aes(y = weekly_hours_viewed)) + geom_boxplot(fill = "lightblue") + labs(title = "Weekly Hours Viewed Box Plot", y = "Hours")
```

It appears "Weekly Hours Viewed" skews heavily to the lower end of the distribution. This tells me again the data has likely been curated to only include many "average" weeks and a few outliers on the high end of the distribution. It would be strange that the lowest values would be so overly represented. One would think this, as a continuous data category would form a normal distribution. 

I suspect the under-performing weeks were trimmed from the dataset.

```{r}
hist(df$runtime, main = "Runtime Distribution", xlab = "runtime")
summary(df$runtime)
```
Nothing particularly revealing about runtimes other than it would appear the vast majority of representations are films or series with less than 10 cumulative runtime hours.
```{r}
hist(df$weekly_views, main = "Weekly Views Distribution", xlab = "views")
```

View numbers seem to follow a similar pattern. The existence of high outliers indicates weeks of extremely high viewership. Would be interesting to identify these weeks.
```{r}
df[which.max(df$weekly_views), ]
```
The week of 2023-12-17 appears to be the maximum for viewership. This should be taken with a grain of salt considering viewership information does not go back further than June of 2023.

The amount of absent information is starting to impact EDA.

I'm curious about the relationship between viewing hours and the number of views.

```{r}
ggplot(data = df, aes(x = weekly_hours_viewed, y = weekly_views)) + geom_point() + labs(title = "Views vs View Hours", x = "Hours", y = "Views")
```

Obvious correlation there. What others are there?

# Correlation Matrix

```{r}
cor_matrix <- cor(df[, sapply(df, is.numeric)], use = "complete.obs")

library(corrplot)
corrplot(cor_matrix, method = "circle")
```

Here we see the correlation between views and view hours visualized.

More interestingly, there appears to be a negative correlation between Weekly Views/Weekly View Hours and Weekly Rank. Meaning it would appear that as rank increases, view hours and viewership tends to decrease.

This, while strange on face-value, is explained by lower ranking indicating a higher position. A rank of 1 is superior to rank 10. Thus, as rank "decreases," viewership increases.


